A general Nullstellensatz for generalized spaces

### 2019-05-08 paper-qcoh.tex
Remark regarding a more minimal formulation

>>>>

\begin{rem}Both in Scholium~\ref{scholium:nullstellensatz-more-specific} and in
the axiom scheme~\eqref{eq:nullstellensatz}, it suffices to restrict the
disjunction~``$\bigvee_\alpha \alpha$'' to those formulas~$\alpha$ which are of
the form~``$\exists\cdots\exists\_ \varphi$'' with~$\varphi$ of Horn type.
\end{rem}
